---
title: "UV PPE Data Analysis"
output: html_document
---

# Photodiode analysis

First lets do some setup and load in the data

```{r, message=FALSE}
# Load libraries
library(dplyr)
library(stringr)
library(readr)
library(ggplot2)

# Function for pulling all the data in
import_data_set <- function(filenameglob) {
  fileNames <- Sys.glob(filenameglob)
  df <- data.frame()
  for (file in fileNames) {
    temp <- read_csv(file, col_names = FALSE)
    temp$filename <- file
    temp$time <- row.names(temp)
    df <- rbind(df, temp)  

  }
  return(df)
}


# This script assumes it's running next to a directory that contains directories containing data for each hood
# Each hood data directory contains a set of directories of the form h[hood number]_[x_coordinate][y_coordinate]_all_[on/off, indicating whether UV lights were on or off]
# Each of these directories contains a csv file for each sensor, showing its voltage over a series of time points
init_df <- import_data_set("data/*/*/*.csv") 
init_df$time <- as.numeric(as.character(init_df$time))

# The "lights on" files have an extra 100 0-ish data points at the beginning, except the center position in hood 1
init_df <- init_df %>% filter(str_detect(filename, "h1_22") | str_detect(filename, "all_off") | time > 101)
# Make sure everything looks right
ggplot(data=init_df) + geom_point(aes(y=X1, color=str_detect(filename, "all_off"), x=time)) + theme(legend.position = "none")
```

Now we make the heatmap

```{r, message=FALSE}
# Calculate summary statistics
df <- init_df %>% group_by(filename) %>% summarise(mean = mean(X1), min=min(X1), max=max(X1))

# Determine metadata from filepath
df$on <- df$filename %>% str_extract("all_...") %>% str_replace("all_", "") %>% str_replace("/","")
df$y <- df$filename %>% str_extract("_[:digit:][:digit:]") %>% str_sub(3,3)
df$x <- df$filename %>% str_extract("_[:digit:][:digit:]") %>% str_sub(2,2)
df$hood <- df$filename %>% str_extract("/h[:digit:]") %>% str_extract("[:digit:]")
df$sensor <- df$filename %>% str_extract("uv_data[:digit:]") %>% str_extract("[:digit:]")

# Do some gymnastics to put on and off data in the same row so that we can easily subtract out the off data (since we assume that's the baseline voltage that is not due to the UV lights)
df$filename <- NULL
on_df <- df %>% filter(on=="on")
off_df <- df %>% filter(on=="off")
off_df <- off_df %>% mutate(off_mean=mean, off_min=min, off_max = max)
off_df$mean <- NULL
off_df$min <- NULL
off_df$max <- NULL
off_df$on <- NULL
on_df$on <- NULL
df <- merge(on_df, off_df,all.y = TRUE)

# Now do some gymnastics so that we can nest the different positions within the heatmap
df$y <- as.numeric(as.character(df$y))
df$sensor <- as.numeric(as.character(df$sensor))
df$heatmapy <- (df$y-1)*3 + df$sensor-1

df$sensor <- df$sensor %>% recode("1"="bottom", "2"="middle", "3"="top")
df$hood <- df$hood %>% recode("1"="BSC 1", "2"="BSC 3")
df

# Make plot
ggplot(data=df) + geom_raster(aes(x=x,y=heatmapy,fill=mean-off_mean)) + theme_classic() + scale_fill_continuous("Mean voltage", type = "viridis")  + geom_vline(xintercept = 1.5) + geom_vline(xintercept = 2.5) + geom_hline(yintercept = 5.48) + geom_hline(yintercept = 2.48)  + facet_wrap(~hood) + theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), axis.line = element_blank())
ggsave("figs/hood_voltage_heat_map.png", width=7, height=3)
```

Calculate the variation across each mask from photodiode data


```{r message=FALSE}

##calulate the ratio between the max and min measurement for each mask
mask_df<-df %>% group_by(hood, x, y) %>% summarise(min=min(mean-off_mean), max=max(mean-off_mean), ratio=max(mean-off_mean)/min(mean-off_mean))

# Make plot
ggplot(data=mask_df) + geom_raster(aes(x=x,y=3-y,fill=ratio)) + theme_classic() + scale_fill_continuous("max:min", type = "viridis")+facet_wrap(~hood)+ geom_vline(xintercept = 1.5) + geom_vline(xintercept = 2.5) + geom_hline(yintercept = 1.5)  +geom_hline(yintercept = .5) +theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), axis.line = element_blank())
ggsave("hood_vars_heat_map.png", width=7, height=3)


# Calculate summary statistics across entire dataset
max(mask_df$ratio) #maxmium variation 
median(mask_df$ratio) #median variation 
median((mask_df %>% filter(x!=2 &y !=1))$ratio) #median variation for masks not in center column or first row
median((mask_df %>% filter(x!=2 &y ==3))$ratio) #median variation for masks not in center column or first two rows

```

# UV meter analysis

Load the UV meter data and plot it as a heat map.

```{r, message=FALSE}
# Load data
hood_1 <- read_csv("data/hood1/uv_meter.csv",col_names = FALSE)
hood_2 <- read_csv("data/hood3/uv_meter.csv",col_names = FALSE)

# Convert data from matrix format to dataframe format
uv_meter_data <- data.frame(radiation=c(hood_1$X1, hood_1$X2, hood_1$X3, hood_2$X1, hood_2$X2, hood_2$X3))
uv_meter_data$x <- c(1,1,1,2,2,2,3,3,3,1,1,1,2,2,2,3,3,3)
uv_meter_data$y <- rep(c(1,2,3),6)
# The second hood with UV meter measurements is not one we have photodiode measurments for 
uv_meter_data$hood <- c(rep("BSC 1", 9), rep("BSC 2", 9))

# Make plot
ggplot(data=uv_meter_data) + geom_raster(aes(x=x,y=y,fill=radiation)) + theme_classic() + scale_fill_continuous(expression(atop("UV radiation",~(paste(mu,W)/cm^2))), type = "viridis")  + facet_wrap(~hood) + theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), axis.line = element_blank()) + geom_text(aes(x=x,y=y,label=radiation), color="black")
ggsave("figs/uv_meter_heatmap.png", width=7, height=3)
```

Now let's calculate some numbers based on this data

```{r, message=FALSE}
uv_meter_data %>% group_by(hood) %>% summarize(ratio=max(radiation)/min(radiation), min=min(radiation))
```

## Raising the UV meter

We can achieve more UV radiation and thus faster decontamination by elevating N95 masks within BSCs. To understand this possibility, we took some measurements at higher elevations within BSC 1:

```{r, message=FALSE}
# Load data
hood_1 <- read_csv("data/hood1/uv_meter.csv",col_names = FALSE)
hood_1_raised_19 <- read_csv("data/hood1/uv_meter_19_inches.csv",col_names = FALSE)
hood_1_raised_13 <- read_csv("data/hood1/uv_meter_13_inches.csv",col_names = FALSE)
  
uv_meter_data <- data.frame(radiation=c(hood_1$X1, hood_1$X2, hood_1$X3, hood_1_raised_13$X1, hood_1_raised_13$X2, hood_1_raised_13$X3, hood_1_raised_19$X1, hood_1_raised_19$X2, hood_1_raised_19$X3))
uv_meter_data$x <- c(1,1,1,2,2,2,3,3,3,1,1,1,2,2,2,3,3,3,1,1,1,2,2,2,3,3,3)
uv_meter_data$y <- rep(c(1,2,3),9)
# The second hood with UV meter measurements is not one we have photodiode measurments for 
uv_meter_data$hood <- c(rep("Floor", 9), rep("Raised 33 cm", 9), rep("Raised 48 cm", 9))
  
# Make plot
ggplot(data=uv_meter_data) + geom_raster(aes(x=x,y=y,fill=radiation)) + theme_classic() + scale_fill_continuous(expression(atop("UV radiation",~(paste(mu,W)/cm^2))), type = "viridis")  + facet_wrap(~hood) + theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), axis.line = element_blank()) + geom_text(aes(x=x,y=y,label=radiation), color="black")

ggsave("figs/uv_meter_heatmap_raised.png", width=7, height=2.5)
```